\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-07-17 tex/paper.tex
Rajesh and Dustin
reworded last paragraph of intro

In this note, we develop an unsupervised learning algorithm for the point
estimation of the parameters $\bftheta$ of a non-differentiable, implicit
generative model. We adapt the adversarial
training procedure of generative adversarial
networks~\cite{goodfellow2014generative} by replacing the implicit generative
network with a domain-based scientific simulator, and solve the resulting
non-differentiable minimax problem by minimizing variational upper
bounds~\citep{2011arXiv1106.4487W,2012arXiv1212.4507S} of the adversarial
objectives. The procedure results in learning an arbitrarily tight
proposal distribution over simulator parameters, such that the corresponding
marginal distribution of the generated data matches the observations.

@@

We would like to thank Lukas Heinrich for helpful comments regarding
the electron--positron annihilation simulation.
GL and KL are both supported through NSF ACI-1450310, additionally KC is
supported through PHY-1505463 and PHY-1205376.

>>>>

In this note, we develop a likelihood-free inference algorithms 
non-differentiable, implicit generative mode. The first allows us 
to perform empirical Bayes through variational inference, and the 
second provides a point estimator of the parameters $\bftheta$. 
We adapt the adversarial
training procedure of generative adversarial
networks~\cite{goodfellow2014generative} by replacing the implicit generative
network with a domain-based scientific simulator, and solve the resulting
non-differentiable minimax problem by minimizing variational upper
bounds~\citep{2011arXiv1106.4487W,2012arXiv1212.4507S} of the adversarial
objectives. 
The objective of both algorithms is to match marginal distribution of 
the generated data to the empirical distribution of the observations.

%The procedure results in learning an arbitrarily tight
%proposal distribution over simulator parameters, such that the corresponding
%marginal distribution of the generated data matches the observations.

%In this note, we develop an unsupervised learning algorithm for the point
%estimation of the parameters $\bftheta$ of a non-differentiable, implicit
%generative model. We adapt the adversarial
%training procedure of generative adversarial
%networks~\cite{goodfellow2014generative} by replacing the implicit generative
%network with a domain-based scientific simulator, and solve the resulting
%non-differentiable minimax problem by minimizing variational upper
%bounds~\citep{2011arXiv1106.4487W,2012arXiv1212.4507S} of the adversarial
%objectives. 
%The procedure results in learning an arbitrarily tight
%proposal distribution over simulator parameters, such that the corresponding
%marginal distribution of the generated data matches the observations.

@@

We would like to thank Lukas Heinrich for helpful comments regarding
the electron--positron annihilation simulation. We would also like to thank
Rajesh Ranganath and Dustin Tran for enlightening discussions and feedback.
GL and KL are both supported through NSF ACI-1450310, additionally KC is
supported through PHY-1505463 and PHY-1205376.
